Nesta attacks study

### 2021-08-27 paperDraft/paperDraft.tex
typos fixed, some minor changes proposed by Rafal made

This article describes an experimental intervention study based in a
naturalistic, digital setting (Q\&A forum - Reddit), utilizing a
collective intelligence approach to content moderation and reduction of
the level of verbal aggression among a selected group of Reddit users
who regularly attack other community members. Collective Intelligence in
this sense means exploring the collaboration between human and machine
intelligence to develop solutions to social challenges. Artificial
Intelligence was used to detect verbal aggression (personal attacks) and
notify human volunteers about attacks. Volunteers after receiving
notifications employed interventions based on norm or empathy promotion.
We find that only those who were sanctioned with norms-inducing
interventions had their personal attacks' level significantly decreased.

@@

Although much effort has been made in order to tackle the problem of
verbal aggression and harassment online, looking at various reports and
surveys (Laub, 2019; Sorrentino, Baldry, Farrington, \& Blaya, 2019;
Vogels, 2021), it remains a common hindrance for people engaging with
social media in their everyday lives. The problem got exacerbated in the
midst of the COVID19 pandemic\todo{is it less coloquial now?}, during
which a majority of our social life moved to cyberspace. During this
shift, there was an increase in cyberbullying attitudes and perpetration
(Barlett, Simmers, Roth, \& Gentile (2021)), 90\% increase in public
reports of illegal online content Grant (2021), including 114\% increase
in non-consensual sharing of intimate images, 30\% increase in
cyberbullying, as well as 40\% of increase in adults reporting online
harassment.\footnote{The increase is reported as a relative change between the year 2019 and 2020.}
According to a report conducted by company L1ght (L1ght, 2020), hate
speech directed towards China and the Chinese went up by 900\% on
Twitter. Gaming platforms were in the spotlight as well, with a 40\%
increase in toxicity on Discord
\footnote{In this industry report, the increase is reported as a relative change between the year 2019 and 2020 as well, with no absolute indicators.}.

@@

\todo{This deserves a developed paragraph with examples}Lack of
generalisability of the models---an ability to perform well on datasets
coming from sources other than the one used for training is a serious
shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
2019; Yin \& Zubiaga, 2021).

As shown by Wu, Ribeiro, Heer, \& Weld (2019), Lipton \& Steinhardt
(2019), and Musgrave, Belongie, \& Lim (2020) in practice, the
development of such models often lacks thorough error analysis and
legitimate experimental methodology, which can result in
non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being made to a wider public. Specifically, Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike. First,
the inability to draw a clear distinction between speculation and
explanation, with the first one often being disguised as the second. For
instance, in a paper from 2017 (Steinhardt, Koh, \& Liang, 2017), Jacob
Steinhardt, the author of Lipton \& Steinhardt (2019), admitted to
stating that ``the high dimensionality and abundance of irrelevant
features\ldots{} give the attacker more room to construct attacks'' -
although no experiments were conducted to measure what is the effect of
dimensionality of the neural network on its attackability. Second, the
inability of successful identification of the sources of performance
improvement (whether it was problem formulation, optimization of the
heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet
another aspect). As was shown by Gabor Melis, Chris Dyer, and Phil
Blunsom, some improvements in language modeling which originally were
ascribed to complex innovations in the architecture of the network,
stemed from hyperparameter tuning (Melis, Dyer, \& Blunsom, 2017). As
mentioned by Lipton \& Steinhardt (2019), there is a tremendous value
coming from the thorough understanding of a particular method, and a
variety of techniques are vital in the process (like ablation,
robustness checks, qualitative error analysis) for the benefit of the
whole community. Third, ``mathiness''---the use of obscure language and
often covering weak argumentation with the alluring but often apparent
depth of technical jargon. Again Jacob Steinhardt admitted infusing his
2015 paper co-authored with Percy Liang (Steinhardt \& Liang, 2015) with
irrelevant theorem to amplify the empirical results. They discussed
``staged strong Doeblin chains'' which actually had limited pertinence
to the learning algorithm---the main subject of a paper. Last but not
least---misuse of language\todo{Give an example}. This includes
suggestive definitions without proper explanation of what they mean in
the context (e.g.~inflating good performance in simple NLP tasks to
human-level understanding), overloading the papers with technical
terminology, or suitcase words (words that can encompass a variety of
meanings, e.g.~consciousness)

@@

There are different approaches when it comes to the moderation of online
content. One can follow the workflow of reactive moderation, which
happens once the content is published. Harmful messages can be either
reported by the users of the platforms or automated methods and then
sent for review to moderators. A set of actions can be then taken
depending on the platform and their community guidelines---on the
content or user level. A harmful message can be deleted, made invisible
to other users, or certain profanities can be altered with special signs
to censor them. Depending on the type and amount of infraction, a
particular user can be warned, muted or shadowbanned, or banned from
further participation in the community for a period of time. The
weakness of the reactive method is that the damage is done. Whoever is
the recipient of the abusive message has the chance to see it and
potentially suffer Wachs et al. (2019). Yet another weakness connected
with relying solely on human reports is the content that is harmful but
unreported by a receipted or any bystander. Although the exact scale of
unreported content is not known, various self-report studies show that a
lot of children, teens, or even adults do not report cyberbullying or
harassment online ({``Free to {Play}?''} 2020; French, 2021; {``In,''}
2017).

@@

The main objective of the experiment was to test whether the level of
verbal aggression (personal attacks) of a group of users' regularly
attacking others on Reddit can be significantly decreased by
community-driven, counter-speech interventions conducted by volunteers
in partnership with Artificial Intelligence. Instead of using negative
motivation system, the assumption was to test a positive one -
convincing vrbally violent users to refrain from using cyberviolence
based on peer-pressure regulation and experiential learning of a
positive set of norms and empathy. Algorithms developed for the
detection of personal attacks were used to monitor the activity of
experimental groups and notify volunteers about all attacks generated by
its' members. Volunteers, after receiving a notification on Slack
(perhaps say more about those processes and infrastructure), could then
react with the proper intervention. Such an approach served as a
distributed bottom-up voluntary model of moderation based on collective
intelligence - utilizing human + machine intelligence.

In the end, what we were able to compare was the following: the
effectiveness of the existing Reddit moderation system (predominantly
grounded in a punitive authoritarian paradigm) versus the existing
moderation system combined with collective intelligence - Artificial
Intelligence supported with a crowd of volunteers - who introduced the
element of positive peer-pressure.

This was a 6-months field experiment in a digital setting conducted on a
popular Q\&A and news forum, Reddit (www.reddit.com). We formed
treatment and control groups based on three main criteria:
\renewcommand{\labelenumii}{\Roman{enumii}}

\begin{enumerate}
 \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily. Thus, we needed approximately 200 attacks daily generated by the treatment groups.
\item Identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
\item Identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
 \end{enumerate}

\renewcommand{\labelenumii}{\Roman{enumii}}
 \begin{enumerate}
   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe. This resulted in the identification of 93966 users. 
   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string). This resulted in the removal of 388 users, thus 93578 were left on our list.
   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice). As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions. This step resulted in the removal of users below the third quartile (Q3). 20124 users were left in our group.
   \item Moving forward, we removed users who generated less than 14 comments in given week. We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)). This resulted in the removal of 2192 users, so 17932 were left.
   \item We discarded users whose personal attacks to all comments ratio was below 2\%. This means inclusion in the sample above the 1st quartile. 4422 users were removed, leaving us with a group of 13510. 
   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks). During this period we have monitored the activity of the identified group of 13510 users and applied the next selection criteria to make sure we select the regularly active and attacking users. 
   \item The period of monitoring was divided into weeks. We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data). Thus, we have taken into consideration only 6 full weeks for the period.
   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified. First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criteria led to only 255 users left, which was not enough for the study. Less restrictive criteria (at least 1 attack generated during 5/6 weeks) resulted in 694 people. 
   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic). The rest was delegated as a control group (304 users).

@@

@@

\leavevmode\hypertarget{ref-melis2017state}{}%
Melis, G., Dyer, C., \& Blunsom, P. (2017). On the state of the art of
evaluation in neural language models. \emph{arXiv Preprint
arXiv:1707.05589}.

@@

\leavevmode\hypertarget{ref-steinhardt2017certified}{}%
Steinhardt, J., Koh, P. W., \& Liang, P. (2017). Certified defenses for
data poisoning attacks. \emph{Proceedings of the 31st International
Conference on Neural Information Processing Systems}, 3520--3532.

\leavevmode\hypertarget{ref-steinhardt2015learning}{}%
Steinhardt, J., \& Liang, P. (2015). Learning fast-mixing models for
structured prediction. \emph{International Conference on Machine
Learning}, 1063--1072. PMLR.

>>>>

This article describes an experimental intervention study conducted in a
naturalistic, digital setting (Q\&A forum on Reddit), utilizing a
collective intelligence approach to content moderation and reduction of
the level of verbal aggression among a selected group of Reddit users
who regularly attack other community members. Collective Intelligence in
this sense means exploring the collaboration between human and machine
intelligence to develop solutions to social challenges. Artificial
Intelligence was used to detect verbal aggression (personal attacks) and
notify human volunteers about attacks. Volunteers after receiving
notifications employed interventions based on norm or empathy promotion.
We find that only those who were sanctioned with norms-inducing
interventions had their personal attacks' level significantly decreased.

@@

Although much effort has been made in order to tackle the problem of
verbal aggression and harassment online, looking at various reports and
surveys (Laub, 2019; Sorrentino, Baldry, Farrington, \& Blaya, 2019;
Vogels, 2021), it remains a common hindrance for people engaging with
social media in their everyday lives. The problem got exacerbated in the
midst of the COVID19 pandemic, during which the majority of our social
life moved to cyberspace. During this shift, there was an increase in
cyberbullying attitudes and perpetration (Barlett, Simmers, Roth, \&
Gentile, 2021), 90\% increase in public reports of illegal online
content (Grant, 2021), including 114\% increase in non-consensual
sharing of intimate images, 30\% increase in cyberbullying, as well as
40\% of increase in adults reporting online harassment. According to a
report conducted by company L1ght (L1ght, 2020), hate speech directed
towards China and the Chinese went up by 900\% on Twitter. Gaming
platforms were in the spotlight as well, with a 40\% increase in
toxicity on Discord
\footnote{In both reports, the increase is reported as a relative change between the year 2019 and 2020, with no absolute indicators.}.

@@

\todo{This deserves a developed paragraph with examples}Lack of
generalisability of the models---the ability to perform well on datasets
coming from sources other than the one used for training---is a serious
shortcoming as well (Rosa et al., 2019; Swamy, Jamatia, \& Gambäck,
2019; Yin \& Zubiaga, 2021).

As shown by Wu, Ribeiro, Heer, \& Weld (2019), Lipton \& Steinhardt
(2019), and Musgrave, Belongie, \& Lim (2020) in practice, the
development of such models often lacks thorough error analysis and
legitimate experimental methodology, which can result in
non-reproducibility. This is also connected with a potential lack of
thorough understanding of the limitations of the models and spurious
conclusions being announced to a wider public. Specifically, Lipton \&
Steinhardt (2019) distinguishes four dysfunctional patterns occurring in
the current research paradigm in the industry and academia alike.

\renewcommand{\labelenumii}{\Roman{enumii}}
 \begin{enumerate}
\item First, the inability to draw a clear distinction between speculation and explanation, with the first one often being disguised as the second. For instance, in a paper from 2017 [@steinhardt2017certified], Jacob Steinhardt, the author of @lipton2019troubling, admitted to stating that “the high dimensionality and abundance of irrelevant features... give the attacker more room to construct attacks” - although no experiments were conducted to measure what is the effect of dimensionality of the neural network on its attackability. 
\item Second, the inability of successful identification of the sources of performance improvement (whether it was problem formulation, optimization of the heuristics, data-preprocessing, hyperparameter tuning, or perhaps yet another aspect). As was shown by Gabor Melis, Chris Dyer, and Phil Blunsom, some improvements in language modeling which originally were ascribed to complex innovations in the architecture of the network, stem from hyperparameter tuning [@melis2017state]. As mentioned by @lipton2019troubling, there is a tremendous value coming from the thorough understanding of a particular method, and a variety of techniques are vital in the process (like ablation, robustness checks, qualitative error analysis) for the benefit of the whole community.
\item Third, "mathiness"---the use of obscure language and often covering weak argumentation with the alluring but often apparent depth of technical jargon. Again Jacob Steinhardt admitted infusing his 2015 paper co-authored with Percy Liang [@steinhardt2015learning] with an irrelevant theorem to amplify the empirical results. They discussed “staged strong Doeblin chains” which actually had limited pertinence to the learning algorithm---the main subject of a paper. 
\item Last but not least---misuse of language\todo{Give an example}. This includes suggestive definitions without proper explanation of what they mean in the context (e.g. inflating good performance in simple NLP tasks to human-level understanding), overloading the papers with technical terminology, or suitcase words (words that can encompass a variety of meanings, e.g. consciousness) 
 \end{enumerate}

@@

There are different approaches when it comes to the moderation of online
content. One can follow the workflow of reactive moderation, which
happens once the content is published. Harmful messages can be either
reported by the users of the platforms or automated methods and then
sent for review to moderators. A set of actions can be then taken
depending on the platform and their community guidelines---on the
content or user level. A harmful message can be deleted, made invisible
to other users, or certain profanities can be altered with special signs
to censor them. Depending on the type and amount of infraction, a
particular user can be warned, muted, shadowbanned, or banned from
further participation in the community for a period of time. The
weakness of the reactive method is that the damage is done. Whoever is
the recipient of the abusive message has the chance to see it and
potentially suffer Wachs et al. (2019). Yet another weakness connected
with relying solely on human reports is the content that is harmful but
unreported by a receipted or any bystander. Although the exact scale of
unreported content is not known, various self-report studies show that a
lot of children, teens, or even adults do not report cyberbullying or
harassment online ({``Free to {Play}?''} 2020; French, 2021; {``In,''}
2017).

@@

The main objective of the experiment was to test whether the level of
verbal aggression (personal attacks) of a group of users' regularly
attacking others on Reddit can be significantly decreased by
community-driven, counter-speech interventions conducted by volunteers
in partnership with Artificial Intelligence. Instead of using negative
motivation system, the assumption was to test a positive one -
convincing verbally violent users to refrain from using cyberviolence
based on peer-pressure regulation and experiential learning of a
positive set of norms and empathy. Algorithms developed for the
detection of personal attacks were used to monitor the activity of
experimental groups and notify volunteers about all attacks generated by
its' members. Volunteers, after receiving a notification on Slack, could
then react with a proper intervention. Such an approach served as a
distributed bottom-up voluntary model of moderation based on collective
intelligence---utilizing human + machine intelligence.

In the end, what we were able to compare was the following: the
effectiveness of the existing Reddit moderation system (predominantly
grounded in a punitive authoritarian paradigm) versus the existing
moderation system combined with collective intelligence---Artificial
Intelligence supported with a crowd of volunteers---who introduced the
element of positive peer-pressure.

@@

This was a 6-months field experiment in a digital setting conducted on a
popular Q\&A and news forum, Reddit (www.reddit.com). We formed
treatment and control groups based on three main criteria:

\renewcommand{\labelenumii}{\Roman{enumii}}
 \begin{enumerate}
 \item During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily. Thus, we needed approximately 200 attacks daily generated by the treatment groups.
\item The identification of users who regularly attack others was necessary to measure the effect of interventions at the end.
\item The identification of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
 \end{enumerate}

\renewcommand{\labelenumii}{\Roman{enumii}}
 \begin{enumerate}
   \item First, we obtained 1 week of real-time (coming from 15-22nd of February 2020), unmoderated data from Reddit. The content was downloaded from the data stream provided by pushshift.io. 
   \item Samurai Labs Artificial Intelligence for personal attacks detection was applied to identify users who attacked others at least once within the aforementioned timeframe. This resulted in the identification of 93966 users. 
   \item We removed all accounts which we suspected not to be run by humans (AutoModerator and all users which had "bot" in the username string). This resulted in the removal of 388 users, thus 93578 were left on our list.
   \item Next, we removed users who generated only 1 personal attack during the week (leaving only those who attacked at least twice). As mentioned, the group of those regularly attacking others was crucial to measure the effects of the interventions. This step resulted in the removal of users below the third quartile (Q3). 20124 users were left in our group.
   \item Moving forward, we removed users who generated less than 14 comments in this week. We cared about most active users, and 2 comments per day per person on average seemed reasonable (not sure yet how to justify this - 14 comments is below 1st quartile (Q1:28, Q2: 63, Q3:126, mean=103)). This resulted in the removal of 2192 users, so 17932 were left.
   \item We discarded users whose personal attacks to all comments ratio was below 2\%. This means the inclusion in the sample of users above the 1st quartile. 4422 users were removed, leaving us with a group of 13510. 
   \item The next step of the process begun on March 9th, 2020, and lasted until May 5th, 2020 (9 weeks). During this period we have monitored the activity of the identified group of 13510 users and applied further selection criteria to make sure we select those who were regularly active and attacked other users. 
   \item The period of monitoring was divided into weeks. We have discarded those weeks during which technical difficulties occurred with the pushshift.io (resulting in missing data). Thus, we have taken into consideration only 6 full weeks for the period.
   \item Users who generated at least 1 attack during 5 out of 6 weeks were identified. First, we planned to restrict the list to only those users, who generate at least 1 attack during each week (6/6) but such restrictive criterion led to only 255 users left, which was not enough for the study. The less restrictive criterion (at least 1 attack generated during 5/6 weeks) resulted in 694 people. 
   \item Next, we calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day, 1.94 attacks daily per person on average).
   \item Knowing that we need around 200 attacks/daily per treatment group (just enough for volunteers to keep up according to our assumption), we have randomly selected 195 users per each treatment group (normative and empathetic). The rest was delegated as a control group (304 users).

@@

@@
